Predicting political party affiliation from text

### 2016-06-17 manuscript/poltext.tex
:x

\author{Felix Biessmann\thanks{~\tt felix.biessmann@gmail.com}\\
  \And
  Sebastian Schelter \thanks{~\tt sebastian.schelter@tu-berlin.de}\\ Technische Universit\"at Berlin
\And 
Daniel Kirsch
  \And
 Pola Lehmann\thanks{ ~{\tt pola.lehmann@wzb.eu} }\\
  Wissenschaftszentrum Berlin\\
}

>>>>

\author{Felix Biessmann\thanks{~\tt felix.biessmann@gmail.com}\\
    \And
 Pola Lehmann\thanks{ ~{\tt pola.lehmann@wzb.eu} }\\
  Wissenschaftszentrum Berlin\\
\And 
Daniel Kirsch
 \And
  Sebastian Schelter \thanks{~\tt sebastian.schelter@tu-berlin.de}\\ TU Berlin
}
